---
title: "Lab 00 - Hello IDS!"
author: "Cameron Arthur"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Gregor", "Jamie", 
           "Benji", "tom", "Max"),
  github_username = c("mcgregors-garden", "gregor-mackay", "jd43", 
                      "BenjiEdmondson", "tomdsimpson", "maxx-creed"),
  colour = c("powderblue", "navyblue", "purple", 
             "orange", "cadetblue3", "olivedrab"),
  hobby = c("Hopping", "hockey", "taekwondo", "orienteering", "cycling", "guitar"),
  favourite_number = c(2, 7, 4, 9, 3, 4),
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Shows a bar graph of the teams favourite number against their Git username

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username")
         (y = "Favourite Number")
         (Title = "Teams Favourite Number")
```

Labs adds Labels to the axis of the graphs

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
